\documentclass[11pt,a4paper]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{titlesec}
\usepackage{pdfpages}
	\titleformat{\section}[runin]{\normalfont\normalsize\bfseries}{\thesection}{1em}{}
	\titlespacing{\section}{0em}{0em}{1em}
	\titleformat{\subsection}{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
		\titlespacing*{\subsection}{0em}{1em}{0.25em}
\usepackage{natbib}
	\bibliographystyle{harvard}
	\bibpunct{(}{)}{;}{a}{}{,}
	\setcitestyle{super}
\usepackage[bibliography=normal, margins=normal]{savetrees}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{tabto}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{courier}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[colorlinks]{hyperref}
	\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!60!black},
	urlcolor={blue!40!black}
	}
\usepackage[super]{nth}
\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{floatflt}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}
\setlength{\abovecaptionskip}{5pt}


\begin{document}

\subsection*{NSF Biographical Sketch}
	Michael Andrew Jansen
	\\
	Ph.D. Candidate - Evolutionary Biology
	\\
	School of Life Sciences, PO Box 874501, Arizona State University, Tempe, AZ 85287-4501, USA
	\\
	Phone: (480) 727-9692
	\\
	Email: \href{mailto:majanse1@asu.edu}{majanse1@asu.edu}
	
\subsection*{Professional Preparation}
	University of Florida \tabto*{2in} Gainesville, FL \tabto*{3.25in} Entomology and Nematology [B.Sc.] \tabto*{5.5in} 2007-2011
	\\
	Arizona State University \tabto*{2in} Tempe, AZ \tabto*{3.25in} Biology [M.Sc.] \tabto*{5.5in} 2012-2014
	\\
	Arizona State University \tabto*{2in} Tempe, AZ \tabto*{3.25in} Evolutionary Biology [M.Sc.] \tabto*{5.5in} 2014-2017
	\\
	Arizona State University \tabto*{2in} Tempe, AZ \tabto*{3.25in} Evolutionary Biology [Ph.D.] \tabto*{5.5in} 2014-2019

\subsection*{Professional Appointments}
	\begin{tabbing}
		\hspace{5cm}\=\hspace{7.75cm}\=\kill
		\textit{Teaching Appointments}\\
		\hspace{2cm}\=\hspace{6.5cm}\=\hspace{4cm}\=\kill
		\textbf{Course} \> \textbf{Subject} \> \textbf{Semester} \> \textbf{Position}\\
		BIO 386 \> Entomology \> Fall - 2018 \> Instructor \\ 
		BIO 201 \> Human Anatomy and Physiology \> Spring - 2017 \> Teaching Assistant \\
		BIO 281 \> Biology (\nth{1}~Semester) \> Fall - 2016 \> Teaching Assistant \\
		BIO 182 \> Biology (\nth{2}~Semester) \> Summer - 2016 \> Teaching Assistant \\
		BIO 181 \> Biology (\nth{1}~Semester) \> Spring - 2016 \> Teaching Assistant \\
		BIO 386 \> Entomology \> Fall - 2015, 2014, 2013 \> Teaching Assistant \\
		BIO 282 \> Biology (\nth{2}~Semester for Majors) \> Spring 2014 \> Teaching Assistant\\
	\end{tabbing}
	\vspace{-1.5em}
	\textit{Research Fellowships}
	\begin{description}
		\item [2019] ASU School of Life Sciences Completion Fellowship
		\item [2018] ASU Biomimicry Center Fellowship
		\item [2017] ASU Evolutionary Biology Doctoral Program Summer Fellowship
	\end{description}

\subsection*{Publications}
		\begin{description}
		\itemsep0.5em
		\item \textit{Jansen, M.A.} \& N.M. Franz. 2018. Descriptions of four new species of \textit{Minyomerus} Horn, 1876 (Coleoptera: Curculionid\ae), with notes on their distribution and phylogeny. \textit{PeerJ}. \href{https://peerj.com/articles/5633/}{6: e5633.}
		\item \textit{Jansen, M.A.}, Luck, K., Campbell, J., Amor, H.B., \& D. Aukes. 2017. Bio-inspired robot design considering load-bearing and kinematic ontogeny of Chelonioidea sea turtles. In \textit{Biomimetic and Biohybrid Systems}. \href{http://www.springer.com/us/book/9783319635361}{p. 216-229}
		\item Luck, K., \textit{Jansen, M.A.}, Campbell, J., Aukes, D., \& H.B. Amor. 2017. From the lab to the desert: fast prototyping and learning of robot locomotion. \textit{Robotics: Science and Systems}. \textit{Proceedings of Robotics: Science and Systems}. \href{http://www.roboticsproceedings.org/rss13/p75.html}{13: p. 75-83}.
		\item \textit{Jansen, M.A.}, Singh, S.S., Chawla, N., \& N.M. Franz. 2016. A multilayer micromechanical model of the cuticle of \textit{Curculio longinasus} Chittenden, 1927 (Coleoptera: Curculionid\ae). \textit{Journal of Structural Biology}. \href{http://www.sciencedirect.com/science/article/pii/S1047847716300922}{195: p. 139-158.}
		\item Singh, S.S., \textit{Jansen, M.A.}, Franz, N.M., \& N. Chawla. 2016. Microstructure and nanoindentation of the rostrum of \textit{Curculio longinasus} Chittenden, 1927 (Coleoptera: Curculionid\ae). \textit{Materials Characterization}. \href{http://www.sciencedirect.com/science/article/pii/S1044580316301619}{118: p. 206-211.}
	\end{description}

\subsection*{Synergistic Activities}
	\begin{itemize}
		\item Served as biological/biomimicry research specialist on animal communication mechanisms \tabto*{5.65in} 2018-2019
		\\
		Collaboration with ASU Biomimicry Center and Google Advanced Technology and Projects
		\item Co-founded Western Entomological Supply and Western Innovation Research Group \tabto*{5.65in} 2017-2019
		\\
		Design, production, and sale of supplies for mounting and curation of research specimens
		\\
		All designs under MIT License {\textcopyright} 2018, available at: \href{https://github.com/western-entomological}{github.com/western-entomological}
		\item Design, prototyping, and field-testing of autonomous, biomimietic robotic sand-crawlers \tabto*{5.65in} 2016-2019
		\\
		C-Turtle - V1.0 design under CC BY 4.0, available at: \href{https://sites.google.com/view/c-turtle/}{sites.google.com/view/c-turtle/}
		\item US patent application for systems and methods for rapid-prototyped robotic devices. \tabto*{5.65in} 2017-2018
		\\
		\textit{US Patent App. No. 16/215,910}. Filed 11 Dec 2018.
		\textit{US Patent App. No. 62/597,276} Filed 11 Dec 2017.
	\end{itemize}
	
\end{document}